Generative AI for image reconstruction in Intensity Interferometry: a first attempt

### 2025-09-29 Phase_II/draft/ParaGan.tex
fig6

>>>>

The process to train the model is summarized here:
\begin{figure*}[htbp]
	\centering
	\begin{tikzpicture}[node distance=0.9cm]

		% Data pipeline
		\node[block, fill=blue!15] (data) {Ground Truth \\ (Create $N$ Images of Stellar Objects)};
		\node[block, fill=red!10, below=of data] (pre) {Simulation \\ (Intensity Interferometry (II) Data)};
		\node[block, fill=green!20, below=of pre, minimum width=5cm] (split) {Input Dataset (Merge of Ground Truth \\ and Simulation of II) Split \\ (Training, Validation, Testing)};

		% Split branches
		\node[block, fill=green!15, below left=0.6cm and 2.5cm of split] (train) {Training Set \\ (Learn Model Parameters)};
		\node[block, fill=yellow!20, below=0.6cm of split] (val) {Validation Set \\ (Tune Hyperparameters)};
		\node[block, fill=orange!20, below right=0.6cm and 2.5cm of split] (test) {Testing Set \\ (Final Evaluation)};

		% Model training big box
		\node[block, fill=orange!20, below=3cm of val, minimum width=10cm, minimum height=1.2cm] (mod) {Train the Model \\ (Generator + Discriminator)};

		% Generator side (left)
		\node[block, fill=cyan!15, below=1.2cm of mod, xshift=-3.5cm] (noise) {Random Noise $z$};
		\node[block, fill=green!20, below=of noise] (gen) {Generator $G(z)$};
		\node[block, fill=blue!10, below=of gen] (fake) {Generated Image};
		\node[block, fill=purple!20, below=of fake] (gloss) {Generator Loss \\ (Update $G$)};

		% Discriminator side (right)
		\node[block, fill=yellow!20, below=1.2cm of mod, xshift=+3.5cm] (real) {Real Image \\ (From Training Set)};
		\node[block, fill=orange!20, below=of real] (disc) {Discriminator $D(x)$};
		\node[block, fill=red!20, below=of disc] (out) {Output: Real/Fake};
		\node[block, fill=purple!30, below=of out] (dloss) {Discriminator Loss \\ (Update $D$)};

		% Final result block
		\node[block, fill=teal!20, below=4.2cm of val, minimum width=5cm] (res) {Result / Evaluation \\ (Performance Metrics: Accuracy)};

		% Connections for data pipeline
		\draw[arrow] (data) -- (pre);
		\draw[arrow] (pre) -- (split);
		\draw[arrow] (split.south west) |- (train.north);
		\draw[arrow] (split.south) -- (val.north);
		\draw[arrow] (split.south east) |- (test.north);
		\draw[arrow] (train.south) |- (mod.north);

		% GAN arrows
		\draw[arrow] (mod) -- (noise);
		\draw[arrow] (mod) -- (real);
		\draw[arrow] (noise) -- (gen);
		\draw[arrow] (gen) -- (fake);
		\draw[arrow] (fake.east) -- ++(0.5,0) |- (disc.west);
		\draw[arrow] (real) -- (disc);
		\draw[arrow] (disc) -- (out);

		% Feedback loops
		\draw[arrow] (out.south west) -- ++(-3,0) |- (gloss.east);
		\draw[arrow] (gloss.west) -- ++(-3,0) |- (gen.west);
		\draw[arrow] (out.south east) -- ++(3,0) |- (dloss.east);
		\draw[arrow] (dloss.east) -- ++(3,0) |- (disc.east);

		% Validation & Testing to Result
		\draw[arrow] (val.south) -- (res.north);
		\draw[arrow] (test.south) -- (res.north);

	\end{tikzpicture}
	\caption{The cGAN-based image reconstruction block diagram. Data is split into training (used for GAN optimization), validation (for hyperparameter tuning), and testing (for final evaluation). The GAN training loop optimizes Generator and Discriminator, while validation and testing feed into performance evaluation metrics.}
	\label{fig:gan_block}
\end{figure*}

### 2025-09-29 Phase_II/draft/main.tex
for journal
fig6

\documentclass[twocolumn]{emulateapj}

\usepackage{amsmath}
\usepackage[colorlinks=true,
linkcolor=blue,
citecolor=blue,
urlcolor=cyan]{hyperref}

@@

\title{Generative AI for image reconstruction\\ in Intensity Interferometry: a first attempt}

\author{Km Nitu Rai,$^{1,2}$, Yuri van der Burg$^{3}$, Soumen
  Basak$^{1}$, Prasenjit Saha,$^{3}$ and Subrata Sarangi$^{4,5}$}

\affiliation{$^{1}$School of Physics, Indian Institute of Science
  Education and Research Thiruvananthapuram, Maruthamala PO, Vithura,
  Thiruvananthapuram 695551, Kerala, India.}

\affiliation{$^{2}$Aryabhatta Research Institute of Observational Sciences, Manora Peak, Nainital 263129, India.}

\affiliation{$^{3}$Physik-Institut, University of Zurich,
  Winterthurerstrasse 190, 8057 Zurich, Switzerland.}

\affiliation{$^{4}$School of Applied Sciences, Centurion University of
  Technology and Management, Odisha-752050, India.}

\affiliation{$^5$ Visiting Associate, Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411 007, Maharashtra, India.}

@@

\bibliographystyle{aasjournal}
\bibliography{refs}

>>>>

\documentclass[linenumbers, twocolumn]{aastex701}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{shapes, arrows.meta, positioning, calc}

\tikzset{
	block/.style={
		rectangle,
		draw,
		rounded corners,
		minimum height=1cm,
		minimum width=3cm,
		align=center
	},
	arrow/.style={
		thick,
		-{Stealth}
	}
}

@@

\title{Generative AI for image reconstruction in Intensity Interferometry: a first attempt}

\author{Km Nitu Rai}
\affiliation{School of Physics, Indian Institute of Science Education and Research Thiruvananthapuram, Maruthamala PO, Vithura, Thiruvananthapuram 695551, Kerala, India.}
\affiliation{Aryabhatta Research Institute of Observational Sciences, Manora Peak, Nainital 263129, India.}
\email{niturai201296@gmail.com}

\author{Yuri van der Burg} 
\affiliation{Physik-Institut, University of Zurich,	Winterthurerstrasse 190, 8057 Zurich, Switzerland.}
\email{yuri.vanderburg@uzh.ch}

\author{Soumen Basak}
\affiliation{School of Physics, Indian Institute of Science Education and Research Thiruvananthapuram, Maruthamala PO, Vithura, Thiruvananthapuram 695551, Kerala, India.}
\email{sbasak2006@gmail.com}

\author{Prasenjit Saha}
\affiliation{Physik-Institut, University of Zurich,	Winterthurerstrasse 190, 8057 Zurich, Switzerland.}
\email{psaha@physik.uzh.ch}

\author{Subrata Sarangi}
\affiliation{School of Applied Sciences, Centurion University of	Technology and Management, Odisha-752050, India.}
\affiliation{Visiting Associate, Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411 007, Maharashtra, India.}
\email{ssarangi.itech@gmail.com}

@@

\bibliographystyle{aasjournalv7}
\bibliography{refs}
